### 2018-07-29 Sections/optical_routers.tex
Added all dropcaps

Perhaps the most fundamental building block in any network is routers, devices which switch data packets between multiple inputs and outputs so as to relay them to a destination. Indeed, in many real-world networks, many nodes will purely implement routing, and nothing more elaborate such as computations or other end-user protocols, to be discussed in Sec.~\ref{sec:protocols_quant_int}.

>>>>

\dropcap{P}{erhaps} the most fundamental building block in any network is routers, devices which switch data packets between multiple inputs and outputs so as to relay them to a destination. Indeed, in many real-world networks, many nodes will purely implement routing, and nothing more elaborate such as computations or other end-user protocols, to be discussed in Sec.~\ref{sec:protocols_quant_int}.

### 2018-07-29 Sections/optical_stability_in_quantum_networks.tex
Added all dropcaps

Given that communications links in quantum networks are expected to be optical, an issue of central importance is optical stability when signals from remote sources interfere or interact with local quantum states. For example, in an entanglement swapping protocol (Sec.~\ref{sec:swapping}) forming a part of a quantum repeater network (Sec.~\ref{sec:rep_net}), if the entangling operation between the remotely prepared qubits suffers errors, so too will the prepared distributed entangled state.

>>>>

\dropcap{G}{iven} that communications links in quantum networks are expected to be optical, an issue of central importance is optical stability when signals from remote sources interfere or interact with local quantum states. For example, in an entanglement swapping protocol (Sec.~\ref{sec:swapping}) forming a part of a quantum repeater network (Sec.~\ref{sec:rep_net}), if the entangling operation between the remotely prepared qubits suffers errors, so too will the prepared distributed entangled state.

### 2018-07-29 Sections/optimising_the_world.tex
Added all dropcaps

Every aspect of our modern world is heavily optimised to improve efficiency, affordability, profitability, and every other kind of desirability. Even long before the digital revolution, which enabled the widespread implementation of modern optimisation-theoretic techniques, humans have always striven to make life as easy as possible -- the least effort for the greatest possible reward. Our modern application of optimisation theory is merely a logical extension of this to the many other facets of the 21st century economy that now exist.

>>>>

\dropcap{E}{very} aspect of our modern world is heavily optimised to improve efficiency, affordability, profitability, and every other kind of desirability. Even long before the digital revolution, which enabled the widespread implementation of modern optimisation-theoretic techniques, humans have always striven to make life as easy as possible -- the least effort for the greatest possible reward. Our modern application of optimisation theory is merely a logical extension of this to the many other facets of the 21st century economy that now exist.

### 2018-07-29 Sections/quantum_networks.tex
Added all dropcaps

We have reviewed some of the key aspects of classical networks, including the real-world implementation of classical networking via the TCP/IP protocol stack, and the essential mathematical foundations for networking theory, including cost vector analysis and routing strategies.

>>>>

\dropcap{W}{e} have reviewed some of the key aspects of classical networks, including the real-world implementation of classical networking via the TCP/IP protocol stack, and the essential mathematical foundations for networking theory, including cost vector analysis and routing strategies.

### 2018-07-29 Sections/quantum_repeater_networks.tex
Added all dropcaps

In the previous section (Sec.~\ref{sec:ent_ultimate}) we concluded that quantum networks specialising purely in entanglement distribution (Bell-pairs in the simplest case), would already be extremely capable in enabling many distributed quantum protocols. This motivates the development of protocols for entanglement distribution over noisy, long-distance quantum networks.

>>>>

\dropcap{I}{n} the previous section (Sec.~\ref{sec:ent_ultimate}) we concluded that quantum networks specialising purely in entanglement distribution (Bell-pairs in the simplest case), would already be extremely capable in enabling many distributed quantum protocols. This motivates the development of protocols for entanglement distribution over noisy, long-distance quantum networks.

### 2018-07-29 Sections/routing_strategies.tex
Added all dropcaps

In Sec.~\ref{sec:costs} we introduced the notion of network costs, strategies for allocating network resources in Sec.~\ref{sec:route_strats}, and a general formalism for optimising strategies so as to minimise costs in Sec.~\ref{sec:strat_opt}. In this section we present some meaningful example strategies and associated pseudo-code fragments, illustrating the implementation of various aspects of strategies of practical real-world interest.

>>>>

\dropcap{I}{n} Sec.~\ref{sec:costs} we introduced the notion of network costs, strategies for allocating network resources in Sec.~\ref{sec:route_strats}, and a general formalism for optimising strategies so as to minimise costs in Sec.~\ref{sec:strat_opt}. In this section we present some meaningful example strategies and associated pseudo-code fragments, illustrating the implementation of various aspects of strategies of practical real-world interest.

### 2018-07-29 Sections/the_irrelevance_of_latency.tex
Added all dropcaps

Entanglement distribution\index{Entanglement distribution} can be executed in a highly varying manner of ways -- from transmitting optical qubits through space via satellites, to across land surfaces via optical fibre, to dumping solid-state qubits into cargo containers and shipping them via land or sea freight. These bring with them associated transmission latencies. The former two distribute entanglement at the speed of light with latencies on the order of microseconds, whereas the latter induces enormous latencies on the order of days or weeks.

>>>>

\dropcap{E}{ntanglement} distribution\index{Entanglement distribution} can be executed in a highly varying manner of ways -- from transmitting optical qubits through space via satellites, to across land surfaces via optical fibre, to dumping solid-state qubits into cargo containers and shipping them via land or sea freight. These bring with them associated transmission latencies. The former two distribute entanglement at the speed of light with latencies on the order of microseconds, whereas the latter induces enormous latencies on the order of days or weeks.

### 2018-07-29 Sections/the_quantum_space_race.tex
Upgrade texlive2018
Added all dropcaps

One of the major hurdles that must be overcome before quantum networks achieve widespread commercial use is to span large distances between nodes distributing entanglement as a resource. The key technological and commercial centres of the world are decentralised, spread across the globe, hence connections over intercontinental distances are necessary, with nodes separated potentially by thousands of kilometres. This distance is one of the major challenges facing the creation of large-scale quantum networks.

>>>>

\dropcap{O}{ne} of the major hurdles that must be overcome before quantum networks achieve widespread commercial use is to span large distances between nodes distributing entanglement as a resource. The key technological and commercial centres of the world are decentralised, spread across the globe, hence connections over intercontinental distances are necessary, with nodes separated potentially by thousands of kilometres. This distance is one of the major challenges facing the creation of large-scale quantum networks.

### 2018-07-29 Sections/to_the_future_and_beyond.tex
Added all dropcaps

In this part we highlight some of -- in the minds of the authors -- some of the most exciting and transformative applications for the future quantum internet and its monstrous unified quantum computational power. None of the technologies discussed here have presently been realised on any practical scale, but all have revolutionary potential to transform the global economy, how we interact with the world, and how we live our lives.

>>>>

\dropcap{I}{n} this part we highlight some of -- in the minds of the authors -- some of the most exciting and transformative applications for the future quantum internet and its monstrous unified quantum computational power. None of the technologies discussed here have presently been realised on any practical scale, but all have revolutionary potential to transform the global economy, how we interact with the world, and how we live our lives.
